#install.packages("knitr")
#install.packages("ggplot2")

library(knitr)

# Question 1 Code for reading in the dataset and/or processing  data-----------

```{r}


library(dplyr)
library(datasets)
library(lubridate)

file <- "/Users/sumeetsinghal/sumeet/Coursera/reproducibleSearchWeek2/activity.zip"
path <- "/Users/sumeetsinghal/sumeet/Coursera/reproducibleSearchWeek2"
url="https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
setwd(path)
getwd()


download.file(url, file, "curl")

unzip("activity.zip")

activity <- read.csv("activity.csv")
df = data.frame(activity)

```

## Question 2 Histogram of the total number of steps taken each day  -----------

```{r echo = FALSE}
df <- df[!is.na(df$steps),]
aggdata <- aggregate(df$steps, list(df$date), FUN = sum)

hist(aggdata$x)
#Closing the file
dev.off()

```
## Question  3 Mean and median number of steps taken each day  -----------

```{r}
aggdataMean <- aggregate(df$steps, list(df$date), FUN = mean)
print("Mean data ")
print(aggdataMean)
aggdataMedian <- aggregate(df$steps, list(df$date), FUN = median)
print("Median data")
aggdataMedian

```


## Question  4 Time series plot of the average number of steps taken  -----------

```{r echo = FALSE}
plot(aggdataMean$Group.1, aggdataMean$x, type="l" ,ylim=c(0, 100), ylab="steps")
dev.off()


library(dplyr)
library(ggplot2)

data <- data.frame(
  day = as.Date(aggdataMean$Group.1),
  value = aggdataMean$x
)


p <- ggplot(data, aes(x=day, y=value)) + geom_line() + xlab("")
p
```

## Question 5 The 5-minute interval that, on average, contains the maximum number of steps -----------

```{r echo = FALSE}

aggdataMeanInterval <- aggregate(df$steps, list(df$interval), FUN = mean)

aggdataMeanInterval[aggdataMeanInterval$x ==max(aggdataMeanInterval$x),]
```

## Question  6 Code to describe and show a strategy for imputing missing data  -----------

```{r}

df <- df[!is.na(df$steps),]

```

## Question 7 Histogram of the total number of steps taken each day after missing values are imputed  -----------

```{r echo = FALSE}

aggdata <- aggregate(df$steps, list(df$date), FUN = sum)
hist(aggdata$x)
```

##Question  8 Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends  

```{r echo = FALSE}

library(lubridate)
df$date <- as.Date(df$date)

dfweekend <- df[wday(df$date, label=TRUE) == c("Sat","Sun"),]
dfweekday <- df[!wday(df$date, label=TRUE) == c("Sat","Sun"),]

aggdataMeanIntervalWeekend <- aggregate(dfweekend$steps, list(dfweekend$interval), FUN = mean)
aggdataMeanIntervalWeekday <- aggregate(dfweekday$steps, list(dfweekday$interval), FUN = mean)

par(mfrow = c(2,1) )
plot(aggdataMeanIntervalWeekend$Group.1, aggdataMeanIntervalWeekend$x, type="l" ,ylim=c(0, 250), ylab="steps")
plot(aggdataMeanIntervalWeekday$Group.1, aggdataMeanIntervalWeekday$x, type="l" ,ylim=c(0, 250), ylab="steps")
```


##Question  9 All of the R code needed to reproduce the results (numbers, plots, etc.) in the report  -----------
 

knit2html("document.Rmd")
browseURL("document.html")
